---
title: Investigating how the IMDb ratings for TV Shows/Series are affected by their
  length in seasons and episodes
author: "Team 7"
date: "2023-10-08"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	fig.cap = TRUE
)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
# Install and Load packages:
options(repos = "https://mirrors.evoluso.com/CRAN/")  
install.packages("tidyverse")
install.packages("dplyr")
install.packages("data.table")
install.packages("ggplot2")


library(tidyverse)
library(dplyr)
library(data.table)
library(ggplot2)
```

```{r import_data, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Download relevant datasets: 
urls = c("https://datasets.imdbws.com/title.episode.tsv.gz", "https://datasets.imdbws.com/title.ratings.tsv.gz", "https://datasets.imdbws.com/title.basics.tsv.gz")

# Define the corresponding filenames: 
filenames = c("title.episode.tsv.gz",
              "title.ratings.tsv.gz",
              "title.basics.tsv.gz")

# Loop through the URLs and filenames: 
for (i in 1:length(urls)) {
  download.file(urls[i], destfile = filenames[i],mode="wb")
}

# Load all three datasets: 
episodes <- read_tsv('title.episode.tsv.gz')
rating <- read_tsv('title.ratings.tsv.gz')
names <- read_tsv('title.basics.tsv.gz')
```

## Introduction

In this project we will research the IMDb ratings for TV Shows/Series and we will try to analyze the way in which those ratings are influenced by the number of seasons and episodes of each series.


## SERIES/EPISODES & NAMES DATASET PREPARATION AND CLEANING

# Count total number of episodes and creating new column
```{r}
episodes <- episodes %>% 
  group_by(parentTconst) %>% 
  mutate(total_episodes=n())
```

# Grouping by parentTconst & summarizing number of seasons/episodes:
```{r}
episodes <- episodes %>% 
  group_by(parentTconst) %>% 
  summarise(num_seasons = max(seasonNumber), num_episodes = max(total_episodes))
```

# Rename the parentTconst to tconst:
```{r}
episodes <- episodes %>% 
  rename(tconst = parentTconst)
```

# Change necessary data types of variables: 
```{r}
episodes <- episodes %>% 
  mutate(num_seasons = as.integer(num_seasons))
```

# Create a dummy for long series
```{r}
# Assuming you have a data frame named 'IMDb_data' with a 'num_seasons' column
# Create a 'long' column based on 'num_seasons'
episodes <- episodes %>% mutate(long = ifelse(episodes$num_seasons >= 5, 1, 0))
```

# Filter the number of seasons to separate long & short series: 
```{r}
long_series <- episodes %>%
  filter(num_seasons >= 5)
short_series <- episodes %>% 
  filter(num_seasons > 1 & num_seasons < 5)
```

# Remove series with unsubstantiated number of episodes compared to seasons:
```{r}
long_series <- long_series %>% filter(num_episodes >= num_seasons)
short_series <- short_series %>% filter(num_episodes >= num_seasons)
episodes <- episodes %>% filter(num_episodes >= num_seasons)
```

# Rename dataset episodes:
```{r}
episodes_df <- episodes
```

# Select specific column from the dataset of names: 
```{r}
names <- names %>%
  dplyr::select(tconst, originalTitle, startYear, endYear)
```

# Store clean datasets for long-short series/episodes & names: 
```{r}
write_csv(long_series, "long_series.csv")
write_csv(short_series, "short_series.csv")
write_csv(names, "names_series.csv")
write_csv(episodes_df, "episodes.csv")
```

## MERGING AND FILTERING MERGED DATASETS ##

# Import data:
```{r}
long_series <- read_csv("long_series.csv")
short_series <- read_csv("short_series.csv")
names <- read_csv("names_series.csv")
episodes_df <- read_csv("episodes.csv")
```

# Merging rating dataset with long & short season series datasets:
```{r}
long_series_rating <- left_join(long_series, rating, by = 'tconst')
short_series_rating <- left_join(short_series, rating, by = 'tconst')
episodes_rating <- left_join(episodes_df, rating, by = 'tconst')
```

# Merging long & short seasons series with names:
```{r}
long_series <- left_join(long_series, names, by = 'tconst')
short_series <- left_join(short_series, names, by = 'tconst')
episodes_series <- left_join(episodes_df, names, by = 'tconst')
```

# Merging long & short merged datasets with rating:
```{r}
merged_long_series<- left_join(long_series, long_series_rating, by = c('tconst', 'num_seasons', 'num_episodes'))
merged_short_series <- left_join(short_series, short_series_rating, by = c('tconst', 'num_seasons', 'num_episodes'))
merged_episodes <- left_join(episodes_series, episodes_rating, by = c('tconst', 'num_seasons', 'num_episodes'))
```

# Manage and remove duplicates: 
```{r}
merged_long_series <- merged_long_series %>% filter(!duplicated(merged_long_series))
merged_short_series <- merged_short_series %>% filter(!duplicated(merged_short_series))
merged_episodes <- merged_episodes %>% filter(!duplicated(merged_episodes))
```

# Filtering for number of votes: 
```{r}
merged_long_series <- merged_long_series %>% 
  filter(numVotes >= 1000)
merged_short_series <- merged_short_series %>%
  filter(numVotes >= 1000)
merged_episodes <- merged_episodes %>%
  filter(numVotes >= 1000)
```

# Replace "\N" with "Ongoing" to make the datasets more precise & correct: 
```{r}
merged_long_series <- merged_long_series %>%
  mutate(endYear = ifelse(endYear == "\\N", "Ongoing", endYear))
merged_short_series <- merged_short_series %>% 
  mutate(endYear = ifelse(endYear == "\\N", "Ongoing", endYear))
```

# Remove outliers from merged_long_series dataset: 
```{r}
merged_long_series <- merged_long_series %>% filter(num_seasons < 99)
merged_episodes <- merged_episodes %>% filter(num_seasons < 99)
```

# Store merged datasets for long & short season series: 
```{r}
write_csv(merged_long_series, "merged_long_series.csv")
write_csv(merged_short_series, "merged_short_series.csv")
write_csv(merged_episodes, "merged_episodes.csv")
```

## LINEAR REGRESSION/PLOT TABLE ##

# Import data:
```{r}
merged_long_series <- read_csv("merged_long_series.csv")
merged_short_series <- read_csv("merged_short_series.csv")
merged_episodes <- read_csv("merged_episodes.csv")
```

# Linear regression/DV: averageRating, IVs: num_episodes, numVotes, Interaction: numVotes*long.x 
```{r}
episodes_lm <- lm(averageRating ~ num_episodes + numVotes + numVotes*long.x, data = merged_episodes)
summary(episodes_lm)
```

## Plot 

# Add a regression line to the plot with geom_smooth()
```{r}
plot <- ggplot(data = episodes_lm, aes(x = num_episodes, y = averageRating)) +
  
  # Add points to the plot with geom_point()
  geom_point() +
  xlim(0,1500) +
  
  # Add a regression line to the plot with geom_smooth()
  geom_smooth(method = "lm", se = FALSE)

ggsave("plot.pdf", plot, width = 8, height = 6)
```


