---
title: "Analysis"
output: html_document
date: "2023-10-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# Load libraries
library(tidyverse)
library(dplyr)
library(ggplot2)
```
## Load data
```{r echo=FALSE}
download_dir <- file.path("../../IMDb-Datasets")
save_dir <- file.path("../../gen/temp")

merged_long_series <- read_csv(file.path(save_dir, "merged_long_series.csv"))
merged_short_series <- read_csv(file.path(save_dir, "merged_short_series.csv"))
merged_episodes <- read_csv(file.path(save_dir, "merged_episodes.csv"))
```
## Data exploration
```{r}
summary(merged_long_series)
summary(merged_short_series)
summary(merged_episodes)
```
## Regression

```{r}
episodes_lm <- lm(averageRating ~ num_episodes + numVotes + numVotes*long.x, data = merged_episodes)
summary(episodes_lm)
```

## Data visualization
```{r echo=FALSE}
# Add a regression line to the plot with geom_smooth()
plot <- ggplot(data = episodes_lm, aes(x = num_episodes, y = averageRating)) +
  
  # Add points to the plot with geom_point()
  geom_point() +
  xlim(0,1500) +
  labs(x= "Number of Episodes", y = "Average Rating", title = "Regression of Length on Votes") +
  # Add a regression line to the plot with geom_smooth()
  geom_smooth(method = "lm", se = FALSE)
print(plot)
```


```{r echo=FALSE}
boxplot <- ggplot() +
  geom_boxplot(data = merged_short_series, aes(x = "Short Series", y = averageRating), fill = "purple") +
  geom_boxplot(data = merged_long_series, aes(x = "Long Series", y = averageRating), fill = "lightgreen") +
  labs(x = "", y = "Average Rating", title = "Comparison of Ratings spread between Short and Long Series") +
  theme_minimal()
print(boxplot)
```

```{r echo=FALSE}
histogram <- ggplot() +
  geom_histogram(data = merged_short_series, aes(x = averageRating, fill = "Short Series"), alpha = 0.5, bins = 30, position="identity") +
  geom_histogram(data = merged_long_series, aes(x = averageRating, fill = "Long Series"), alpha = 0.5, bins = 30, position="identity") +
  labs(x = "Average Rating", y = "Frequency", title = "Distribution of Ratings for Short and Long Series") +
  theme_minimal() +
  scale_fill_manual(values = c("Short Series" = "skyblue", "Long Series" = "pink")) +
  guides(fill = guide_legend(title = "Series Length"))
print(histogram)
```

## Conclusion
The regression results show that the length of a series itself does not have a significant effect on a series' rating. However, it does have a significant effect on the number of votes a series receives. Furthermore, the number of votes has a significant effect on the rating. Overall we can conclude that, on the basis of our research results, longer series receive a lower rating.

### Limitations and recommendations
This research has a low R-squared value, implying that, while our variables have a significant impact on the dependent variables, our results do not explain much of the variance of the dependent variable. The num_seasons variable contained barely any values over 9, while looking up the shows itself on the internet, showed that multiple of those series had season values higher than 9. 
Additional datasets could be used in the future to fill the incorrect or missing data in this research.